Light inextensible strings under tension in the Schwarzschild geometry

### 2019-02-28 string_ajp.tex
include strings passing through (2,0)
try to include all the graphs
another diagram

>>>>

\begin{figure}[p]
\centering
\includegraphics{angle_at_r_equals_2.pdf} % created by "angle_at_r_equals_2.R"
\caption{Strings passing through $(2,0)$}
\label{strings_r_equals_2}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics{light_start_at_r_equals_2.pdf} % created by "angle_start_at_r_equals_2.R"
\caption{Null geodesics passing through $(2,0)$, shown for $0\leq\phi\leq 2\pi$}
\label{light_r_equals_2}
\end{figure}

\begin{figure}[p] % created by "one_free_end_r_equals_2.R"
\centering
\includegraphics[width=170mm]{one_free_end_r_equals_2.pdf}
\caption{Strings passing through $(2,0)$ tangential to event horizon}
\label{one_free_end_r_equals_2}
\end{figure}
